%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
{Senior iOS Developer} % Job title
{Farfetch (\url{https://farfetch.com}) } % Organization
{Lisbon, Portugal} % Location
{April. 2017 - PRESENT} % Date(s)
{
	\begin{cvitems} % Description(s) of tasks/responsibilities
		\item {Worked on multiple iOS projects from storefront assistant app to the main shoppers' app with millions of active users and a 4.9 rating.}
	 	\item {Key player in building and maintaining the main iOS app using Xcode and Swift.\\}
	 	\url{https://apps.apple.com/pt/app/farfetch-shop-luxury-fashion/id906698760?l=en-GB}
	 	\item {Led multiple innitiatives, from brainstorm to delivery, interacting with stakeholders}
		\item{Built several usefull tools and automations to improve self and peers  (devs, QAs, PMs, Data analysts...) workflows and increase their productivity - Web, iOS, scripting}
		\item {Helping, teaching, sharing and inspiring other developers to bring out their best work}
		\item{Mentored a junior developer since his first day}
	\end{cvitems}
}

  \cventry
    {iOS Developer} % Job title
    {Globestamp (\url{https://globestamp.com}) } % Organization
    {Lisbon, Portugal} % Location
    {April 2016 - March 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      	\item{iOS development using Xcode and Swift}
        \item {Responsible for the whole life cycle development of the Globestamp iOS application.}
        \item {Responsible for mentoring the back-end developer exposing the best API and practices possible.}
        \item {Requirements analysis on both the application and API behaviour.\\}
		\url{https://itunes.apple.com/app/id1031240627}
	 	\item {Git source control (hosting service: Bitbucket)}
      \end{cvitems}
    }

  \cventry
	{iOS Developer} % Job title
    {Waterdog (\url{http://waterdog.mobi/}) } % Organization
    {Lisbon, Portugal} % Location
    {August 2016 - October 2016} % Date(s)
    {
	\begin{cvitems} % Description(s) of tasks/responsibilities
		\item {Small participation in ECO project using Xcode and Swift. ECO (\url{https://eco.pt/}) is a Portuguese newspaper\\}
		\url{https://itunes.apple.com/app/id1031240627}
		\item {Git source control (hosting service: Bitbucket)}
	\end{cvitems}
}

  \cventry
	{Software Developer} % Job title
    {Linkedcare (\url{https://linkedcare.com}) } % Organization
	{Lisbon, Portugal} % Location
	{January 2012 - March 2016} % Date(s)
	{
	 \begin{cvitems} % Description(s) of tasks/responsibilities
	 	\item {Developed software on the health field with the objective of providing better health system for everyone.}
	 	\item{\textbf{Jan 2012 - Nov 2012}}
	 	\item{Web development using Java language, GWT framework, PostgreSql database, Tomcat and JBoss as web servers.}
	 	\item {SVN source control}
	 	\item{\textbf{Nov 2012 - Jan 2015}}
	 	\item{Web development using Ruby language, Ruby on Rails framework, PostgreSql database. Also on the front end used Javascript language and jQuery}
	 	\item{During this time also experimented a little bit of AngularJS and ReactJS}
	 	\item{Extracted monolithic application features into microservices}
	 	\item{Developed internal tools to automate some processes. Issues management for example}
	 	\item{Responsible for customer tickets management, asigning bug to rightful developers}
	 	\item{Responsible for production issues management, assigning them to responsible developers}
	 	\item {Git source control (hosting service: Github)}
	 	\item{\textbf{Jan 2015 - Mar 2016}}
	 	\item{iOS development using Apple's Swift language and Xcode IDE}
	 	\item {Git source control (hosting service: Github)}
	\end{cvitems}
	}

  \cventry
    {Inov Contacto Trainee } % Job title
    {LatitudeN (\url{https://latituden.com}) } % Organization
    {Darmstadt, Germany} % Location
    {January 2011 - July 2011} % Date(s)
    {
	\begin{cvitems} % Description(s) of tasks/responsibilities
      	\item {Web development using Java, GWT, CSS, SQlite, JDBC.}
		\item {Developed an internal content management web application.}
		\item {CVS source control\\\\}
	\end{cvitems}
}

%---------------------------------------------------------
\end{cventries}
